---
title: "Knee_Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE}
library(plyr)
#library(papeR)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(tidyr)
# library(foreign)
# library(multcomp)
# library(broom)
library(nlme)
library(tidyverse)
library(readxl)
library(data.table)

myboxplot = function(x, type = 'Survey'){
  if(endsWith(x, '.Avg')){
    type = 'Diagnosis'
  }
  df = dplyr::filter(Data_Long, Measure == x)
  means = aggregate(Score ~ Group, df, mean)
  means$Score = round(means$Score, digits = 2)
    p = ggplot(df, aes(x=Group, y=Score,  fill = Group)) +
    geom_boxplot() +
    geom_dotplot(binaxis='y', stackdir='center',  dotsize=.9, fill = 'grey')+
    labs(title = paste(str_remove(x, '.Avg'), type))
    
   if (type == 'Survey'){
      p = p + geom_text(data = means, aes(label = Score, y = -.5, size = 1.5, fontface='bold'))+
        scale_y_continuous(limits = c(-.5,10),breaks=seq(0,10,2))
   }else{
     p = p + geom_text(data = means, aes(label = Score, y = -.1, size = 1.3, fontface='bold'))+
              scale_y_continuous(limits = c(-.1,1),breaks=seq(0,1,.2))+
             ylab('Percentage')
   }
  p = p + theme_classic()+
  theme(plot.title = element_text(color= 'black',face='bold',size=18))+
   theme(axis.title.x = element_text(color= 'black',face='bold',size=18),
        axis.text.x = element_text(color= 'black',face='bold',size=18))+
  theme(axis.title.y = element_text(color= 'black',face='bold',size=18),
        axis.text.y = element_text(color= 'black',face='bold',size=18))+
 theme(legend.text = element_text( size = 18, face = "bold"))+
theme(legend.position="none")+
    theme(# adjust X-axis labels; also adjust their position using margin (acts like a bounding box)
          # using margin was needed because of the inwards placement of ticks
          # http://stackoverflow.com/questions/26367296/how-do-i-make-my-axis-ticks-face-inwards-in-ggplot2
          axis.text.x = element_text( margin = unit(c(t = 2.5, r = 0, b = 0, l = 0), "mm")),
          # adjust Y-axis labels
          axis.text.y = element_text( margin = unit(c(t = 0, r = 2.5, b = 0, l = 0), "mm")),
          # length of tick marks - negative sign places ticks inwards
          axis.ticks.length = unit(-1.4, "mm"),
          # width of tick marks in mm
          axis.ticks = element_line(size = .8))
print(p)
# t-test
pre.measure = paste0('Pre.',x)
post.measure = paste0('Post.',x)
print(paste('paired t-test of',pre.measure, '&', post.measure))
print(t.test(as.vector(as.matrix(Data[pre.measure])), as.vector(as.matrix(Data[post.measure])),  paired = TRUE))
}


singleboxplot = function(x){
df = drop_na(dplyr::select(Data, x))
means = round(mean(df[,1]), digits = 2)
print(ggplot(data = df, aes(x='', y=unlist(df), fill = 'blue')) +
    geom_boxplot() +
    geom_dotplot(binaxis='y', stackdir='center',  dotsize=.9, fill = 'grey')+
 labs(title = paste(i))+
  ylab('Score')+ xlab('')+
  theme(legend.position = 'none')+
   scale_y_continuous(limits = c(-.5,10),breaks=seq(0,10,2))+
  geom_text( aes(label = means, y = -.5, size = 1.5, fontface='bold'))+
   theme_classic()+
  theme(plot.title = element_text(color= 'black',face='bold',size=18))+
   theme(axis.title.x = element_text(color= 'black',face='bold',size=18),
        axis.text.x = element_text(color= 'black',face='bold',size=18))+
  theme(axis.title.y = element_text(color= 'black',face='bold',size=18),
        axis.text.y = element_text(color= 'black',face='bold',size=18))+
 theme(legend.text = element_text( size = 18, face = "bold"))+
theme(legend.position="none")+
    theme(# adjust X-axis labels; also adjust their position using margin (acts like a bounding box)
          # using margin was needed because of the inwards placement of ticks
          # http://stackoverflow.com/questions/26367296/how-do-i-make-my-axis-ticks-face-inwards-in-ggplot2
          axis.text.x = element_text( margin = unit(c(t = 2.5, r = 0, b = 0, l = 0), "mm")),
          # adjust Y-axis labels
          axis.text.y = element_text( margin = unit(c(t = 0, r = 2.5, b = 0, l = 0), "mm")),
          # length of tick marks - negative sign places ticks inwards
          axis.ticks.length = unit(-1.4, "mm"),
          # width of tick marks in mm
          axis.ticks = element_line(size = .8)))

}
```


# Pre data sheet
Subject

## 1.I feel prepared to perform the following diagnostic knee examination techniques
  PreValgus 
  PreVarus
  PreLach
  PrePD
  PreAD
  PreLever
2. CurrentKnowledge
3. ClinicalSetting
5. FutureCareer

## Station Diagnostic responses:
Station1
Station2
Station3
Station4
Station5
Station6
Station7
Station8

## Competency Checklist for injury side and non-injury side. 1 = completed 0 = not completed 
Valgus1Injury
Valgus2Injury
Valgus3Injury
Valgus1NonInjury
Valgus2NonInjury
Valgus3NonInjury
Varus1Injury
Varus2Injury
Varus3Injury
Varus1NonInjury
Varus2NonInjury
Varus3NonInjury
Lach1Injury
Lach2Injury
Lach3Injury
Lach1NonInjury
Lach2NonInjury
Lach3NonInjury
PD1Injury
PD2Injury
PD3Injury
PD1NonInjury
PD2NonInjury
PD3NonInjury
AD1Injury
AD2Injury
AD3Injury
AD1NonInjury
AD2NonInjury
AD3NonInjury
Lever1Injury
Lever2Injury
Lever3Injury
Lever1NonInjury
Lever2NonInjury
Lever3NonInjury

## Stand alone quesitons, previous experience questions:
4. PreviousThiel
6. PreviousDiagnostic


## Import Predata and add station key
Station 1 - MCL
Station 2 - LCL
Station 3 - PCL
Station 4 - No Injury (Sham)
Station 5 - ACL, LCL
Station 6 - ACL, PCL
Station 7 - ACL
Station 8 - ACL, MCL

## Add pre post comparison by station two bar graph, shows percentage of pre and post with t-test. 

```{r}
PreData = read_excel('PreData.xlsx')
# Diagnosis Key
PreData$Station1Key = 'MCL'
PreData$Station2Key = 'LCL'
PreData$Station3Key = 'PCL'
PreData$Station4Key = 'No Injury'
PreData$Station5Key = 'ACL, LCL'
PreData$Station6Key = 'ACL, PCL'
PreData$Station7Key = 'ACL'
PreData$Station8Key = 'ACL, MCL'
```

## Make avg scores of diagnosis and compentency checklist

```{r}
# Diagnosis check
PreData$Station1Result = with(PreData, Station1 == Station1Key)
PreData$Station2Result = with(PreData, Station2 == Station2Key)
PreData$Station3Result = with(PreData, Station3 == Station3Key)
PreData$Station4Result = with(PreData, Station4 == Station4Key)
PreData$Station5Result = with(PreData, Station5 == Station5Key)
PreData$Station6Result = with(PreData, Station6 == Station6Key)
PreData$Station7Result = with(PreData, Station7 == Station7Key)
PreData$Station8Result = with(PreData, Station8 == Station8Key)

# Create avg station diagnosis accuracy
Result.list = colnames(dplyr::select(PreData,Station1Result:Station8Result))
PreData$Pre.Station.Avg = rowSums(PreData[Result.list], na.rm = TRUE)/length(Result.list)
  
# Create Checklist avg
Result.list = colnames(dplyr::select(PreData,Valgus1Injury:Lever3NonInjury))
PreData$Pre.Competency.Avg = rowSums(PreData[Result.list], na.rm = TRUE)/length(Result.list)

# Create avg score for all measures
Measures = c('Valgus', 'Varus', 'Lach', 'PD', 'AD', 'Lever')
PreData$Pre.Valgus.Avg = NA
PreData$Pre.Varus.Avg = NA
PreData$Pre.Lach.Avg = NA
PreData$Pre.PD.Avg = NA
PreData$Pre.AD.Avg = NA
PreData$Pre.Lever.Avg = NA
for (M in Measures) {
  measure1 = paste0(M, '1Injury')
  measure2 = paste0(M, '3NonInjury')
  colTitle = paste0('Pre.',M, '.Avg')
  Result.list = colnames(dplyr::select(PreData,all_of(measure1): all_of(measure2)))
  PreData[colTitle] = rowSums(PreData[Result.list], na.rm = TRUE)/length(Result.list)
}
```


## Import PostData
__________________________________________
# Post data sheet
Subject

## 1.	I feel prepared to perform the following diagnostic knee examination techniques - Compare to same questions from Pre
PostValgus
PostVarus
PostLach
PostPD
PostAD
PostLever

6. CurrentKnowledge
9. ClinicalSetting
7. FutureCareer

## Station Diagnostic responses:
Station1
Station2
Station3
Station4
Station5
Station6
Station7
Station8

## Compentency Checklist for injury side and non-injury side. 1 = completed 0 = not completed or incorrect
Valgus1Injury
Valgus1Injury
Valgus2Injury
Valgus3Injury
Valgus1NonInjury
Valgus2NonInjury
Valgus3NonInjury
Varus1Injury
Varus2Injury
Varus3Injury
Varus1NonInjury
Varus2NonInjury
Varus3NonInjury
Lach1Injury
Lach2Injury
Lach3Injury
Lach1NonInjury
Lach2NonInjury
Lach3NonInjury
PD1Injury
PD2Injury
PD3Injury
PD1NonInjury
PD2NonInjury
PD3NonInjury
AD1Injury
AD2Injury
AD3Injury
AD1NonInjury
AD2NonInjury
AD3NonInjury
Lever1Injury
Lever2Injury
Lever3Injury
Lever1NonInjury
Lever2NonInjury
Lever3NonInjury

## Stand alone quesitons, previous experience questions:
2. GainedNew
3. Improved
4. Effective
8. Retained
9. Transferable


```{r}
PostData = read_excel('PostData.xlsx')
# Diagnosis Key
PostData$Station1Key = 'MCL'
PostData$Station2Key = 'LCL'
PostData$Station3Key = 'PCL'
PostData$Station4Key = 'No Injury'
PostData$Station5Key = 'ACL, LCL'
PostData$Station6Key = 'ACL, PCL'
PostData$Station7Key = 'ACL'
PostData$Station8Key = 'ACL, MCL'
```

## Make avg scores of diagnosis and compentency checklist

```{r}
# Diagnosis check
PostData$Station1Result = with(PostData, Station1 == Station1Key)
PostData$Station2Result = with(PostData, Station2 == Station2Key)
PostData$Station3Result = with(PostData, Station3 == Station3Key)
PostData$Station4Result = with(PostData, Station4 == Station4Key)
PostData$Station5Result = with(PostData, Station5 == Station5Key)
PostData$Station6Result = with(PostData, Station6 == Station6Key)
PostData$Station7Result = with(PostData, Station7 == Station7Key)
PostData$Station8Result = with(PostData, Station8 == Station8Key)

# Create avg station diagnosis accuracy
Result.list = colnames(dplyr::select(PostData,Station1Result:Station8Result))
PostData$Post.Station.Avg = rowSums(PostData[Result.list], na.rm = TRUE)/length(Result.list)
  
# Create Checklist avg
Result.list = colnames(dplyr::select(PostData,Valgus1Injury:Lever3NonInjury))
PostData$Post.Competency.Avg = rowSums(PostData[Result.list], na.rm = TRUE)/length(Result.list)

# Create avg score for all measures
Measures = c('Valgus', 'Varus', 'Lach', 'PD', 'AD', 'Lever')
PostData$Post.Valgus.Avg = NA
PostData$Post.Varus.Avg = NA
PostData$Post.Lach.Avg = NA
PostData$Post.PD.Avg = NA
PostData$Post.AD.Avg = NA
PostData$Post.Lever.Avg = NA
for (M in Measures) {
  measure1 = paste0(M, '1Injury')
  measure2 = paste0(M, '3NonInjury')
  colTitle = paste0('Post.',M, '.Avg')
  Result.list = colnames(dplyr::select(PostData,all_of(measure1): all_of(measure2)))
  PostData[colTitle] = rowSums(PostData[Result.list], na.rm = TRUE)/length(Result.list)
}
```

## Merge Pre and Post data sets

```{r}
# Prep Data for merge
# Prenames = colnames(PreData)
# Postnames = colnames(PostData)
# intersect(Prenames, Postnames)
# PreData$Group = factor('Pre')
# PostData$Group = factor('Post')

setnames(PreData, c('CurrentKnowledge', "ClinicalSetting",  "FutureCareer"), 
                    c('Pre.CurrentKnowledge',"Pre.ClinicalSetting",  "Pre.FutureCareer"))

setnames(PreData, c("PreValgus","PreVarus","PreLach","PrePD","PreAD","PreLever"), 
         c("Pre.Valgus","Pre.Varus","Pre.Lach","Pre.PD","Pre.AD","Pre.Lever"))

setnames(PostData, c("PostValgus","PostVarus","PostLach","PostPD","PostAD", "PostLever" ),
         c("Post.Valgus","Post.Varus","Post.Lach","Post.PD","Post.AD", "Post.Lever"))

setnames(PostData, c('CurrentKnowledge', "ClinicalSetting",  "FutureCareer"), 
                    c('Post.CurrentKnowledge',"Post.ClinicalSetting",  "Post.FutureCareer"))

PreVars = c("Subject","Pre.Valgus","Pre.Varus","Pre.Lach","Pre.PD","Pre.AD","Pre.Lever","Pre.CurrentKnowledge", "Pre.ClinicalSetting","Pre.FutureCareer",
            "Pre.Station.Avg","Pre.Competency.Avg","Pre.Valgus.Avg","Pre.Varus.Avg","Pre.Lach.Avg","Pre.PD.Avg","Pre.AD.Avg","Pre.Lever.Avg",
            "PreviousThiel","PreviousDiagnostic")

PostVar = c( "Subject","Post.Valgus","Post.Varus","Post.Lach","Post.PD","Post.AD", "Post.Lever","Post.CurrentKnowledge", "Post.ClinicalSetting",
             "Post.FutureCareer", "Post.Station.Avg","Post.Competency.Avg","Post.Valgus.Avg","Post.Varus.Avg","Post.Lach.Avg","Post.PD.Avg",
             "Post.AD.Avg","Post.Lever.Avg","GainedNew","Improved","Effective","Retained","Transferable")


Data = merge (PreData[PreVars], PostData[PostVar], by = 'Subject')

# replace N/A with NA
Data[Data=='N/A'] = NA

Data = as.data.frame(lapply(Data, as.numeric))
# colnames(Data_Long)
# Pivot Longer
Data_Long = pivot_longer(Data, 
                         cols = Pre.Valgus:Pre.Lever.Avg,
                         names_to = c('Group',"Measure"), 
                         names_sep = 4, 
                         values_to = 'Score')

Data_Long2 = pivot_longer(Data, 
                         cols = Post.Valgus:Post.Lever.Avg,
                         names_to = c('Group',"Measure"), 
                         names_sep = 5, 
                         values_to = 'Score')

Data_Long = merge(Data_Long[c('Subject','Group', 'Measure', 'Score')], Data_Long2[c('Subject','Group', 'Measure', 'Score')], all = TRUE)
rm(Data_Long2)


Data_Long$Group = factor(gsub('\\.', '', Data_Long$Group), levels = c('Pre', 'Post')) # remove period, needs \\ to escape . function
Data_Long$Measure = factor(Data_Long$Measure)
```

## Statstical Anlaysis

### Survey and Diagnosis Results Change
```{r}
myMeasures= as.character(unique(Data_Long$Measure))
for (i in myMeasures) {
  myboxplot(i)
}


```


### Survey and Diagnosis Results Grand Mean Change
```{r}

t.test(filter(Data_Long, Group == "Pre")$Score, filter(Data_Long, Group == "Post")$Score, paired = TRUE)

t.test(dplyr::filter(Data_Long, Group == 'Pre', Measure %in% c('AD', 'Lach', 'Lever', 'PD', 'Valgus', 'Varus'))$Score, )


```

## Grand Mean of all Surveys of diagnosis technique and performance, stats and plot
```{r}
# Colors midnight and gold

df = dplyr::filter(Data_Long, Measure %in% c('AD', 'Lach', 'Lever', 'PD', 'Valgus', 'Varus'))
  means = aggregate(Score ~ Group, df, mean)
  means$Score = round(means$Score, digits = 2)
  StandD = aggregate(Score ~ Group, df, sd)
  Pre_M_SD = '4.42 (2.35)'
  Post_M_SD = '8.35 (1.66)'
    p = ggplot(df, aes(x=Group, y=Score,  fill = Group)) +
    geom_boxplot() +
      scale_fill_manual(values = c('navyblue', 'gold'))+
    labs(title = paste('Mean Survey Pre and Post'))+
    annotate('text', x = 1, y = 0,  fontface = 'bold', label = Pre_M_SD)+
    annotate('text', x = 2, y = 0,  fontface = 'bold', label = Post_M_SD)
    
   p = p + scale_y_continuous(limits = c(-.5,10),breaks=seq(0,10,2))
   
  p = p + theme_classic()+
  theme(plot.title = element_text(color= 'black',face='bold',size=18))+
   theme(axis.title.x = element_text(color= 'black',face='bold',size=18),
        axis.text.x = element_text(color= 'black',face='bold',size=18))+
  theme(axis.title.y = element_text(color= 'black',face='bold',size=18),
        axis.text.y = element_text(color= 'black',face='bold',size=18))+
 theme(legend.text = element_text( size = 18, face = "bold"))+
theme(legend.position="none")+
    theme(# adjust X-axis labels; also adjust their position using margin (acts like a bounding box)
          # using margin was needed because of the inwards placement of ticks
          # http://stackoverflow.com/questions/26367296/how-do-i-make-my-axis-ticks-face-inwards-in-ggplot2
          axis.text.x = element_text( margin = unit(c(t = 2.5, r = 0, b = 0, l = 0), "mm")),
          # adjust Y-axis labels
          axis.text.y = element_text( margin = unit(c(t = 0, r = 2.5, b = 0, l = 0), "mm")),
          # length of tick marks - negative sign places ticks inwards
          axis.ticks.length = unit(-1.4, "mm"),
          # width of tick marks in mm
          axis.ticks = element_line(size = .8))
print(p)

t.test(dplyr::filter(df, Group == "Pre")$Score, dplyr::filter(df, Group == "Post")$Score, paired = TRUE)

# Diagnosis section 
df = dplyr::filter(Data_Long, Measure %in% c('AD.Avg', 'Lach.Avg', 'Lever.Avg', 'PD.Avg', 'Valgus.Avg', 'Varus.Avg'))
  means = aggregate(Score ~ Group, df, mean)
  means$Score = round(means$Score, digits = 2)
  StandD = aggregate(Score ~ Group, df, sd)
    Pre_M_SD = '0.84 (0.31)'
  Post_M_SD = '0.81 (0.30)'
  p = ggplot(df, aes(x=Group, y=Score,  fill = Group)) +
    geom_boxplot() +
      scale_fill_manual(values = c('navyblue', 'gold'))+
    labs(title = paste('Mean Diagnosis Pre and Post'))+ 
    annotate('text', x = 1, y = -.05,  fontface = 'bold', label = Pre_M_SD)+
    annotate('text', x = 2, y = -.05,  fontface = 'bold', label = Post_M_SD)
    
   p = p + scale_y_continuous(limits = c(-.1,1),breaks=seq(0,1,.2))+
             ylab('Percentage')

  p = p + theme_classic()+
  theme(plot.title = element_text(color= 'black',face='bold',size=18))+
   theme(axis.title.x = element_text(color= 'black',face='bold',size=18),
        axis.text.x = element_text(color= 'black',face='bold',size=18))+
  theme(axis.title.y = element_text(color= 'black',face='bold',size=18),
        axis.text.y = element_text(color= 'black',face='bold',size=18))+
 theme(legend.text = element_text( size = 18, face = "bold"))+
theme(legend.position="none")+
    theme(# adjust X-axis labels; also adjust their position using margin (acts like a bounding box)
          # using margin was needed because of the inwards placement of ticks
          # http://stackoverflow.com/questions/26367296/how-do-i-make-my-axis-ticks-face-inwards-in-ggplot2
          axis.text.x = element_text( margin = unit(c(t = 2.5, r = 0, b = 0, l = 0), "mm")),
          # adjust Y-axis labels
          axis.text.y = element_text( margin = unit(c(t = 0, r = 2.5, b = 0, l = 0), "mm")),
          # length of tick marks - negative sign places ticks inwards
          axis.ticks.length = unit(-1.4, "mm"),
          # width of tick marks in mm
          axis.ticks = element_line(size = .8))
print(p)

t.test(dplyr::filter(df, Group == "Pre")$Score, dplyr::filter(df, Group == "Post")$Score, paired = TRUE)

```

### Correlations

#### Measure performance change with survey performance change
e.g. (preVarugs - PostVargus) correlate with (PreVargus.Avg - PostVargus.Avg)

## Stand Alone Measures: 

Pre= "PreviousThiel","PreviousDiagnostic" 
post =  "GainedNew","Improved", "Effective","Retained","Transferable"

```{r}
myMeasures = c("PreviousThiel","PreviousDiagnostic", "GainedNew","Improved", "Effective","Retained","Transferable")
for (i in myMeasures) {
  singleboxplot(i)
}
# make post surveys in teal?

```

